SSRP Report based on *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019)

### 2024-02-15 other/ssrp/ssrp_report.qmd
Added to ssrp

The statistical programming language R was used to acquire, clean, and process the data [@citeR]. In particular, the following R packages were used: tidyverse [@tidyverse], readxl [@readxl], haven [@haven], ggthemes [@ggthemes], and ggplot2 [@ggplot2].

>>>>

To reproduce figures from *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019), the statistical programming language R was used to acquire, clean, and process the data [@citeR]. In particular, the following R packages were used: tidyverse [@tidyverse], readxl [@readxl], haven [@haven], ggthemes [@ggthemes], and ggplot2 [@ggplot2].
